---
title: Post 5
author: Team HAK
date: '2022-11-11'
slug: []
categories: []
tags: []
description: ~
toc: yes
authors: []
series: []
lastmod: '2022-11-11T21:45:32-05:00'
featuredVideo: ~
featuredImage: ~
---

We are in the process of combining the dataset in our previous post to a 2019-2020
season total analysis dataset. You can find a reference to it here: https://www.basketball-reference.com/leagues/NBA_2020.html

```{r}
library(tidyverse)
teamadvance <- read.csv(here::here("dataset-ignore", '../dataset-ignore/19-20 nba advance data in cvs form.csv'))
team100toal <- read_csv(here::here("dataset-ignore", '../dataset-ignore/19-20 nba total 100 data.csv'))
teamadvance %>%
  mutate(win_rec50 = ifelse(W >=41, 'YES', 'NO'))%>%
  ggplot(aes(x = Age, fill = win_rec50)) +
  geom_histogram(binwidth = 0.5, color = 'black') +
  labs(x = 'Age', y = 'number of teams')
```



```{r}
teamadvance %>%
  mutate(winrate = W/(W+L))%>%
  mutate(win_rec50 = ifelse(W >=41, 'YES', 'NO'))%>%
  ggplot(aes(x = Age, y = winrate,color = win_rec50)) +
  geom_point() +
  geom_smooth(method = 'lm', se = FALSE)
```

```{r}
teamadvance %>% 
  mutate(winrate = W/(W+L))%>%
  mutate(win_rec50 = ifelse(W >=41, 'YES', 'NO'))%>%
  ggplot(aes(x = X3PAr, y = ORtg, color = win_rec50)) +
  geom_point() +
  geom_smooth(method = 'lm', se = FALSE)
```

```{r}
teamadvance %>%
  mutate(winrate = W/(W+L))%>%
  mutate(win_rec50 = ifelse(W >=41, 'YES', 'NO'))%>%
  ggplot(aes(x = ORB., y = DRtg, color = win_rec50)) +
  geom_point() +
  geom_smooth(method = 'lm', se = FALSE)
```

```{r}
teamadvance %>%
  mutate(winrate = W/(W+L))%>%
  mutate(win_rec50 = ifelse(W >=41, 'YES', 'NO'))%>%
  ggplot(aes(x = DRB., y = DRtg, color = win_rec50)) +
  geom_point() +
  geom_smooth(method = 'lm', se = FALSE)
```

Analysis:

From these graphs we have learned that 3 point percentages contribute greatly to 
a teams offensive rating in teams that have at least a 50% win rate. 
Additionally, we found that offensive rebounds do not contribute to defensive
team ratings for all teams. Further, we found a negative correlation between 
defensive rating and defensive rebounds. 