---
title: Post 4
author: Team HAK
date: '2022-11-04'
slug: []
categories: []
tags: []
description: ~
toc: yes
authors: []
series: []
lastmod: '2022-11-04T22:22:57-04:00'
featuredVideo: ~
featuredImage: ~
---

Additionally, now is a good time to start thinking about statistical modeling. What response variable are you interested in? What predictor variables? Are there transformations of columns that you’d need to do to create interesting predictors? What type of model do you want to fit? Linear? Logistic? Or something else?

For this week’s blog post, discuss both going deeper and broader into your EDA and your initial thoughts and results for modeling. As always, make lots of plots and try different types of plots. However, for this week’s post, only include at most 2 figures/tables/output for your EDA and at most 1 figure/table/output for the modeling. Try to put together figures that illustrate the main lesson’s you’ve learned this week.

Response variables of interest: 
Win rate 

Predictor variables of interest: 
FG%
FT%
Point distribution among players in a team
home team advantage, 
win percentage, 
rebounds, assists, turnovers, steals, blocks, plus/minus score, 
offensive rating, defensive rating, and true shooting percentage

Models of interest:
Random Forest

```{r}
library(tidyverse)
data <- read_csv(here::here("dataset-ignore", "../dataset-ignore/2019-20_pbp.csv"))
```

OFFENSIVE REBOUNDS PER WIN 

```{r}
(offensive_reb_away <- data %>% 
  filter(WinningTeam == AwayTeam) %>%
  filter(ReboundType == 'offensive') %>%
  filter(!is.na(AwayPlay))%>%
  group_by(URL)%>%
  summarise(rebounds=n(),AwayPlay)
  )


(offensive_reb_home <- data %>% 
  filter(ReboundType == 'offensive') %>%
  filter(!is.na(HomePlay))%>%
  filter(WinningTeam == HomeTeam) %>%
  group_by(URL)%>%
  summarise(rebounds=n(),HomePlay)
  )

offensive_reb_away <- unique(offensive_reb_away)
offensive_reb_home <- unique(offensive_reb_home)
```

```{r}

names(offensive_reb_home)[3] <- 'play'
names(offensive_reb_away)[3] <- 'play'

offensive_rebounds <- merge(offensive_reb_home,offensive_reb_away,by=c("URL","rebounds","play"),all=TRUE)

offensive_rebounds
```




